\centering{Investigating the Fermi motion effects on the incoherent DVCS channel}

### 2017-02-25 eg6-letters/coherent/dvcs_he4_prl.tex
added a subdirectory for eg6 comments on the coherent paper and another subdirectory for the incoherent channel inestigation.

%
\date{\today}
\begin{abstract}
We report the first fully exclusive measurement of coherent Deeply Virtual Compton 
Scattering off a nucleus for $A>1$. The experiment used the 6 GeV 
electron beam from the CEBAF machine at Jefferson Lab incident on a $^4$He gas 
target in the center of the CEBAF Large Acceptance Spectrometer. A new 
Radial Time Projection Chamber was used to detect the recoiling $^4$He
nuclei and ensure the exclusivity of the process. The measured Beam Spin 
Asymmetries are larger than that observed on the proton in 
the same kinematic domain. Since $^4$He is a spin zero target, we were able to 
extract, in a completely model independent way, the real and imaginary parts of the $^4$He Compton Form Factors, $\cal H_A$, which are functions of the Generalized Parton Distribution $H_A$. 
This pioneering measurement of coherent Deeply Virtual Compton Scattering on the $^4$He nucleus, with a fully exclusive final state via nuclear recoil tagging, leads the way toward 3D imaging of the partonic structure of nuclei.
\end{abstract}
\pacs{Valid PACS appear here}

@@

Rich information on Quantum Chromodynamics (QCD) can be extracted from the internal structure 
of hadrons. In the recent past, development of the Generalized Parton 
Distributions (GPDs) framework has offered a possibility to obtain new 
information about the momentum and spatial degrees of freedom of the quarks and 
gluons inside hadrons 
\cite{Mueller:1998fv,Ji:1996ek,Ji:1996nm,Radyushkin:1996nd,Radyushkin:1997ki}.
In impact parameter space, the GPDs are indeed interpreted as a tomography of the 
transverse plane for partons carrying a certain longitudinal momentum 
\cite{Burkardt:2000za,Diehl:2002he,Belitsky:2002ep,Burkardt:2005hp}.

The most promising way to access GPDs experimentally is through the measurement 
of Deep Virtual Compton Scattering (DVCS), i.e.  the hard exclusive 
electroproduction of a real photon.  While other processes are known to be 
sensitive to GPDs, the measurement of DVCS is considered the cleanest probe and 
has been the focus of worldwide efforts 
\cite{Stepanyan:2001sm,Airapetian,Chekanov:2003ya,Aktas:2005ty,Chen:2006na,Munoz 
Camacho:2006hx,Girod:2007aa,Mazouz:2007aa,Gavalian:2009,Seder:2015,Pisano:2015,Jo:2015ema} 
involving several accelerator facilities such as Jefferson Lab (JLab), HERA and  
CERN.  The vast majority of these measurements focused on the study of proton 
structure and allowed extraction of the tomography of the nucleon (for details 
on the formalism, see 
\cite{Goeke:2001tz,Diehl:2003ny,Ji:2004gf,Belitsky:2005qn,Boffi:2007yc,Guidal:2013rya}).
This framework is also applicable to nuclei, giving access to completely new 
information about nuclear structure in terms of quarks and 
gluons \cite{Dupre:2015jha}.
Study of the 3D structure of nuclei appears to be especially important
in light of the large nuclear effects observed in nuclear parton distribution 
functions \cite{Geesaman:1995yd,Norton:2003cb,Hen:2016kwk}.

\begin{figure}[tb]
\includegraphics[width=6.5cm]{figs/DVCS_diagram.pdf}
\caption{Representation of the leading order handbag diagram of the 
DVCS process off $^4$He.}
\label{fig:diags}
\end{figure}

One must overcome two major experimental challenges in measuring coherent 
nuclear DVCS, $eA\rightarrow^\prime A^\prime\gamma$. First, the cross section 
of coherent scattering is suppressed due to the nuclear form factor, and 
second, the recoil nucleus ($A^\prime$) must be detected to ensure coherence. 
Figure \ref{fig:diags} 
illustrates the hand bag diagram for coherent DVCS on $^4$He.  Similar to the 
proton case, at large virtual photon's 4-momentum square $Q^2=-(k-k')^{2}$ and 
small squared momentum transfer $t=(p-p')^{2}$ (in terms of the electron, 
$k(k')$, and $^4$He, $p(p')$, four-vectors), the DVCS handbag diagram can be 
factorized into two parts \cite{Freund_Collins,Ji_Osborne}. The hard part 
includes the photon-quark interaction and is calculable in perturbative QCD.  
The non-perturbative part is parametrized in terms of GPDs, which embed the 
partonic structure of the hadron. The GPDs depend on the three variables $x$, 
$\xi$ and $t$ as introduced in Figure \ref{fig:diags}. The parameter $\xi$
relates to the Bjorken variable $x_{B}$: $\xi\approx {{x_B}\over{2-x_B}}$, 
where $x_B=\frac{Q^2}{2M\nu}$ with $M$ the proton mass and  
$\nu=k^0-k^{0\prime}$, the $t$ is squared momentum transfer to the target. The 
parameter $x$ is the quark's internal loop momentum fraction and cannot be 
accessed experimentally. In the experiment we measure Compton Form
Factors (CFF) \cite{Guidal:2013rya}, complex amplitudes defined as:

@@

Until now, the only available data on nuclear DVCS was from the 
HERMES experiment \cite{Ellinghaus:2002zw}, where coherence in the reaction was based only on 
kinematic cuts on the measured scattered electron and real photon. That 
measurement was performed on a large set of nuclei ($^4$He, N, Ne, Kr and Xe), 
but the mixing of the coherent and incoherent processes could affect the
measurement significantly \cite{Guzey:2003jh}. In this regard, direct detection 
of the low-energy recoil nucleus is the best way to guarantee the nucleus 
remains intact and that the reaction did not occur on a bound nucleon. The 
CEBAF Large Acceptance Spectrometer (CLAS) in Hall-B at JLab is already 
optimized for DVCS measurements 
\cite{Girod:2007aa,Gavalian:2009,Seder:2015,Pisano:2015,Jo:2015ema}.

@@

The experiment E08-024 took place in Hall-B at Jefferson Lab in 2009 using the 
nearly 100\% duty factor, longitudinally polarized electron beam (83$\%$ 
polarization) at energy of 6.064 GeV. The data were collected over 40 days 
using a 6 atm gaseous $^4$He target placed 64 cm upstream of the nominal center of CLAS. For DVCS 
experiments, the CLAS baseline design \cite{Mecking:2003zu} is supplemented 
with an inner calorimeter (IC) and a solenoid. The IC extends the photon 
detection acceptance of CLAS to polar angles as low as 4$^{\circ}$. The 
low-energy M\o{}ller electrons produced in the target form a very high rate 
background that is suppressed by a 5 Tesla solenoid placed around the target.

In our kinematics, the recoil $^4$He nuclei produced in DVCS have a low average 
momentum around 300 MeV/c. CLAS cannot detect such low energy $\alpha$ 
particles, so in order to ensure the exclusivity of the measurement, we built a 
small and light RTPC to complement CLAS. In Figure~\ref{fig:RTPC} a picture of 
RTPC installed in the experimental hall, and the rendering showing detector 
components and the $^4$He detection concept are presented. The $^4$He gaseous 
target, a $25$ cm long Kapton straw with $27~\mu$m thick wall, was part of the RTPC
assembly and installed on the axis of the detector. The RTPC was calibrated specifically for the detection 
of $^4$He nuclei using elastic scattering with a 1.2~GeV electron beam.

@@

To ensure the interaction occurs at the partonic level and the DVCS handbag 
diagram is dominant, we select events with $Q^{2}>1~[GeV^{2}/c^{2}]$.  
Exclusivity of the coherent DVCS reaction is optimized by applying a set of 
cuts on the following kinematic variables: the co-planarity angle ($\Delta 
\phi$), \textit{i.e.}, the angle between the ($\gamma,\gamma^*$) and 
($\gamma^*,^4He'$) planes, the missing energy, the missing mass squared, the 
missing transverse momentum of the $e'^4He'\gamma$ system, the missing mass 
squared of the $e'^4He'$ system, and the angle ($\theta$) between the measured 
photon and the missing momentum of the $e'^4He'$ system. The most relevant of 
these cuts are presented in Figure~\ref{fig:kin-cuts}, which shows 3$\sigma$ 
cuts except for the missing energy (which appears to be too large and for which 
we reduced the cut window to [-0.45,0.5] GeV).  We also reject events where a 
$\pi^0$ is identified by invariant mass reconstruction of two photons.  After 
these requirements, we have about 3200 DVCS events left, and Figure 
\ref{fig:kin-coverage} presents their kinematic distributions in 
($Q^{2}$,$x_{B}$) and ($Q^{2}$,$-t$).

@@

The DVCS and well-known Bethe-Heitler (BH) processes, where the real 
photon is emitted by the incoming or the outgoing lepton, have the same final 
state and are indistinguishable. The amplitude of real photon 
electroproduction is a sum of the amplitudes of these two processes. The BH 
amplitude is defined by the target form factors, while the DVCS amplitude is 
a combination of the form factors and GPDs. At our kinematics, the cross 
section of real photon electroproduction is dominated by the BH 
contribution, while the DVCS contribution is very small. Its effect is however
enhanced in the observables sensitive to the interference term, {\it e.g.} 
beam spin asymmetry. The three terms entering the cross section calculation,
the BH and DVCS amplitudes squared and their interference term, 
can be decomposed into a finite sum of Fourier harmonics in the azimuthal angle
$\phi$ between the $(e,e^\prime)$ and $(\gamma^*,^4$He$^\prime)$ planes, as
shown for the nucleon in \cite{Belitsky:2001ns} and for the spin-zero targets
in \cite{Kirchner:2003wt,Belitsky:2008bz}. Based on this work, the beam-spin 
asymmetry ($A_{LU}$) of a spin-zero hadron can be expressed as:
\begin{equation}
\begin{split}
&A_{LU}(\phi) = \\
&\frac{\alpha_{0}(\phi) \, \Im m(\mathcal{H}_{A})}
{\alpha_{1}(\phi) + \alpha_{2}(\phi) \, \Re e(\mathcal{H}_{A}) + \alpha_{3}(\phi) \, 
\big( \Re e(\mathcal{H}_{A})^{2} + \Im m(\mathcal{H}_{A})^{2} \big)},
\end{split}
\label{eq:A_LU-coh}
\end{equation}
where $\Im m(\mathcal{H}_{A})$ and $\Re e(\mathcal{H}_{A})$ are the imaginary 
and real parts of the $^4$He CFF $\mathcal{H}_{A}$ that depends on the GPD 
$H_A$. In Eq.~\ref{eq:A_LU-coh}, $\phi$ is the azimuthal angle between the 
($e$,$e'$) and ($\gamma^{*}$,$^4$He$'$) planes. The kinematic factors $\alpha_i$
depend on azimuthal angle $\phi$, the nuclear form factor 
$F_A(t)$, $Q^2$ and $x_B$. These factors are written as:
\begin{align}
   \alpha_0 (\phi) & = \frac{x_{A}(1+\epsilon^2)^2}{y} S_{++}(1) \sin(\phi), \\
   \alpha_1 (\phi) & = c_0^{BH}+c_1^{BH} \cos({\phi})+c_2^{BH} \cos(2\phi), \\ 
   \alpha_2 (\phi) & = \frac{x_{A}(1+\epsilon^2)^2}{y}  \left( 
      C_{++}(0) +  C_{++}(1) cos(\phi) \right), \\
   \alpha_3 (\phi) &= \frac{x^{2}_{A}t(1+\epsilon^2)^2}{y} {\mathcal P}_1(\phi) 
      {\mathcal P}_2(\phi) \cdot 2 \frac{2-2y+y^2 + \frac{\epsilon^2}{2}y^2}{1 + 
      \epsilon^2},
\end{align}
where $x_{A} = \frac{x_{B}M_{N}}{M_{A}}$ with $M_{A}$($M_{N}$) is the $^4$He 
(nucleon) mass, $\epsilon = \frac{2x_{A}M_{A}}{\sqrt{Q^{2}}}$ and 
$y=\frac{Q^{2}}{2x_{A}M_{A}E_{beam}}$, $\mathcal{P}_1(\phi)$ and $\mathcal 
{P}_2(\phi)$ are the Bethe-Heitler propagators. The factors $c_{0,1,2}^{BH}$, 
$c_0^{DVCS}$, $c_{0,1}^{INT}$ and $s_1^{INT}$ are the Fourier coefficients of 
the BH, and $S_{++}(1)$, $C_{++}(0)$, and $C_{++}(1)$ are the Fourier harmonics 
in the leptonic tensor.  The explicit expressions of these terms can be found 
in \cite{Belitsky:2008bz} and show that, by using the $\sin(\phi)$ and 
$\cos(\phi)$ contributions, it is possible to extract $\Im m(\mathcal{H}_{A})$ 
and $\Re e(\mathcal{H}_{A})$ from the beam spin
asymmetry.

@@

The $Q^2$, $X_B$, and $t$ dependencies of the $^4$He CFF $\mathcal{H}_A$ 
extracted from the fit to the azimuthal dependence of $A_{LU}$ are shown in 
Figure \ref{fig:CFF_HA}. Curves on the graphs are model calculations, labelled 
{\it convolution} and {\it off-shell}. In the convolution model 
\cite{Vadim_priv}, the nucleus is assumed to be composed of non-relativistic 
nucleons, each interacting independently with 
the probe. The Convolution-Dual model is based on nucleon GPDs from the dual 
parametrization \cite{Guzey:2006xi}, where the Convolution-VGG uses nucleon 
GPDs  from the VGG model and is based on the double distributions ansatz 
\cite{DD_model}. The off-shell model \cite{GonzalezHernandez:2012jv} relies on 
the impulse approximation and uses advanced spectral functions of  nuclei that 
account for all configurations of the final nuclear system and the binding 
effects between the nucleons.

>>>>

%
\date{\today}
\begin{abstract}
We report the first fully exclusive measurement of coherent deeply virtual 
Compton scattering off a nucleus for $A>1$. The experiment used the 6 GeV 
electron beam from the CEBAF machine at Jefferson Lab incident on a $^4$He gas 
target in the center of the CEBAF large acceptance spectrometer. A new radial 
time projection chamber (RTPC) was used to detect the recoiling $^4$He
nuclei and ensure the exclusivity of the process. The measured beam spin 
asymmetries are larger than that observed on the proton in the same kinematic 
domain. Since $^4$He is a spin zero target, we were able to extract, in a 
completely model independent way, the real and imaginary parts of the $^4$He 
Compton form factors, $\cal H_A$, which are functions of the generalized parton 
distribution $H_A$. This pioneering measurement of coherent deeply virtual 
Compton scattering on the $^4$He nucleus, with a fully exclusive final state 
via nuclear recoil tagging, leads the way toward 3D imaging of the partonic 
structure of nuclei.
\end{abstract}
\pacs{Valid PACS appear here}

@@

Rich information on quantum chromodynamics (QCD) can be extracted from the 
internal structure of hadrons. In the recent past, development of the 
generalized parton distribution (GPD) framework has offered a possibility to 
obtain new information about the momentum and spatial degrees of freedom of the 
quarks and gluons inside hadrons 
\cite{Mueller:1998fv,Ji:1996ek,Ji:1996nm,Radyushkin:1996nd,Radyushkin:1997ki}.
In impact parameter space the GPDs are indeed interpreted as a tomography of 
the transverse plane for partons carrying a certain longitudinal momentum 
\cite{Burkardt:2000za,Diehl:2002he,Belitsky:2002ep,Burkardt:2005hp}.

The most promising way to access GPDs experimentally is through the measurement 
of deeply virtual Compton scattering (DVCS), \textit{i.e.}, the hard exclusive 
electroproduction of a real photon.  While other processes are known to be 
sensitive to GPDs, the measurement of DVCS is considered the cleanest probe and 
has been the focus of worldwide efforts 
\cite{Stepanyan:2001sm,Airapetian,Chekanov:2003ya,Aktas:2005ty,Chen:2006na,Munoz 
Camacho:2006hx,Girod:2007aa,Mazouz:2007aa,Gavalian:2009,Seder:2015,Pisano:2015,Jo:2015ema} 
involving several accelerator facilities such as Jefferson Lab, HERA and  CERN.  
The vast majority of these measurements focused on the study of proton 
structure and allowed for extraction of the three-dimensional picture of the 
nucleon (for details on the formalism, see 
\cite{Goeke:2001tz,Diehl:2003ny,Ji:2004gf,Belitsky:2005qn,Boffi:2007yc,Guidal:2013rya}).
This framework is also applicable to nuclei, giving access to completely new 
information about nuclear structure in terms of quarks and 
gluons \cite{Dupre:2015jha}.
Study of the 3D structure of nuclei appears to be especially important
in light of the large nuclear effects observed in nuclear parton distribution 
functions \cite{Geesaman:1995yd,Norton:2003cb,Hen:2016kwk}.

\begin{figure}[tb]
\includegraphics[width=6.5cm]{figs/DVCS_diagram.pdf}
\caption{Representation of the leading order hand-bag diagram of the DVCS 
process off $^4$He.}
\label{fig:diags}
\end{figure}

One must overcome two major experimental challenges in measuring coherent 
nuclear DVCS, $eA\rightarrow^\prime A^\prime\gamma$. First, the cross section 
of coherent scattering is suppressed due to the nuclear form factor, and 
second, the recoil nucleus ($A^\prime$) must be detected to ensure coherence.  
FIG.~\ref{fig:diags} illustrates the hand-bag diagram for coherent DVCS on 
$^4$He. Similar to the proton case, at large virtual photon's 4-momentum square 
$Q^2=-(k-k')^{2}$ and small squared momentum transfer $t=(p-p')^{2}$ (in terms 
of the electron, $k(k')$, and $^4$He, $p(p')$, four-vectors), the DVCS handbag 
diagram can be factorized into two parts \cite{Freund_Collins,Ji_Osborne}. The 
hard part includes the photon-quark interaction and is calculable in 
perturbative QCD. The non-perturbative part is parametrized in terms of GPDs, 
which embed the partonic structure of the hadron. The GPDs depend on the three 
variables $x$, $\xi$, and $t$ as introduced in FIG.~\ref{fig:diags}. The 
parameter $\xi$ relates to the Bjorken variable $x_{B}$: $\xi\approx 
{{x_B}\over{2-x_B}}$, where $x_B=\frac{Q^2}{2M\nu}$, $\nu=k^0-k^{0\prime}$, and 
$M$ is the proton mass. The parameter $x$ is the quark's internal loop momentum 
fraction and cannot be accessed experimentally. In the experiment we measure 
Compton form factors (CFF) \cite{Guidal:2013rya}, for which their real and 
complex amplitudes are defined at leading order as:

@@

Until now, the only available data on nuclear DVCS was from the HERMES 
experiment \cite{Ellinghaus:2002zw}, where coherence in the reaction was based 
only on kinematic cuts on the measured scattered electron and real photon. That 
measurement was performed on a large set of nuclei ($^4$He, N, Ne, Kr and Xe), 
but the mixing of the coherent and incoherent processes could affect the
measurement significantly \cite{Guzey:2003jh}. In this regard, direct detection 
of the low-energy recoil nucleus is the best way to guarantee that the nucleus 
remains intact. The CEBAF large acceptance spectrometer (CLAS) in Hall-B at 
Jefferson Lab has been previously used for DVCS measurements on nucleon
\cite{Girod:2007aa,Gavalian:2009,Seder:2015,Pisano:2015,Jo:2015ema}.

@@

The experiment E08-024 took place in Hall-B at Jefferson Lab in 2009 using the 
nearly 100\% duty factor, longitudinally polarized electron beam (83$\%$ 
polarization) at an energy of 6.064 GeV. The data were collected over 40 days 
using a 6 atm gaseous $^4$He target placed 64 cm upstream of the nominal center 
of CLAS. For DVCS experiments, the CLAS baseline design \cite{Mecking:2003zu} 
is supplemented with an inner calorimeter (IC) and a solenoid magnet. The IC 
extends the photon detection acceptance of CLAS to polar angles as low as 
4$^{\circ}$. The low-energy M\o{}ller electrons produced in the target form a 
very high rate background that is suppressed by a 5 Tesla solenoid magnet 
placed around the target.

In our kinematics, the recoil $^4$He nuclei produced in DVCS have a low average 
momentum around 300 MeV/c. CLAS cannot detect such low energy $\alpha$ 
particles, so in order to ensure the exclusivity of the measurement, we built a 
small and light RTPC to complement CLAS. Presented in FIG.~\ref{fig:RTPC} are a 
picture of RTPC installed in the experimental hall and a diagram showing the 
basic detection technique. The $^4$He gaseous target, a $25$ cm long Kapton 
straw with $27~\mu$m thick wall, was part of the RTPC assembly and installed on 
the axis of the detector. The RTPC was calibrated specifically for the 
detection of $^4$He nuclei using elastic scattering with a 1.2~GeV electron 
beam.

@@

To ensure the interaction occurs at the partonic level and the DVCS handbag 
diagram is dominant, we select events with $Q^{2}$ greater than 1 
$[GeV^{2}/c^{2}]$. Exclusivity of the coherent DVCS reaction is optimized by 
applying a set of cuts on the following kinematic variables: the co-planarity 
angle ($\Delta \phi$), \textit{i.e.}, the angle between the ($\gamma,\gamma^*$) 
and ($\gamma^*$,$^4$He$'$) planes, the missing energy, the missing mass 
squared, the missing transverse momentum of the $e'^4$He$'\gamma$ system, the 
missing mass squared of the $e'^4$He$'$ system, and the angle ($\theta$) 
between the measured photon and the missing momentum of the $e'^4$He$'$ system.  
The most relevant of these cuts are presented in Figure~\ref{fig:kin-cuts}, 
which shows 3$\sigma$ cuts except for the missing energy (which appears to be 
too large and for which we reduced the cut window to [-0.45,0.5] GeV).  We also 
reject events where a $\pi^0$ is identified by invariant mass reconstruction of 
two photons.  About 3200 events pass these requirements and are shown in 
FIG.~\ref{fig:kin-coverage} as their kinematic distributions in 
($Q^{2}$,$x_{B}$) and ($Q^{2}$,$-t$).

@@

The DVCS and well-known Bethe-Heitler (BH) processes, where the real 
photon is emitted by the incoming or the outgoing lepton, have the same final 
state and are indistinguishable. The amplitude of real photon 
electroproduction is a sum of the amplitudes of these two processes. The BH 
amplitude is defined by the target form factors, while the DVCS amplitude is 
a combination of the form factors and GPDs. At our kinematics, the cross 
section of real photon electroproduction is dominated by the BH 
contribution, while the DVCS contribution is very small. Its effect is however
enhanced in the observables sensitive to the interference term, {\it e.g.} 
beam spin asymmetry. The three terms entering the cross section calculation,
the BH and DVCS amplitudes squared and their interference term, 
can be decomposed into a finite sum of Fourier harmonics in the azimuthal angle
$\phi$ between the $(e,e^\prime)$ and $(\gamma^*,^4$He$^\prime)$ planes, as
shown for the nucleon in \cite{Belitsky:2001ns} and for the spin-zero targets
in \cite{Kirchner:2003wt,Belitsky:2008bz}. Based on this work, the beam-spin 
asymmetry ($A_{LU}$) of a spin-zero hadron can be expressed as:
\begin{equation}
\begin{split}
&A_{LU}(\phi) = \\
&\frac{\alpha_{0}(\phi) \, \Im m(\mathcal{H}_{A})}
{\alpha_{1}(\phi) + \alpha_{2}(\phi) \, \Re e(\mathcal{H}_{A}) + \alpha_{3}(\phi) \, 
\big( \Re e(\mathcal{H}_{A})^{2} + \Im m(\mathcal{H}_{A})^{2} \big)},
\end{split}
\label{eq:A_LU-coh}
\end{equation}
where $\Im m(\mathcal{H}_{A})$ and $\Re e(\mathcal{H}_{A})$ are the imaginary 
and real parts of the $^4$He CFF $\mathcal{H}_{A}$ that depend on the GPD 
$H_A$. In Eq.~\ref{eq:A_LU-coh}, $\phi$ is the azimuthal angle between the 
($e$,$e'$) and ($\gamma^{*}$,$^4$He$'$) planes. The kinematic factors 
$\alpha_i$
depend on azimuthal angle $\phi$, the nuclear form factor 
$F_A(t)$, $Q^2$ and $x_B$. These factors are written as:
\begin{align}
   \alpha_0 (\phi) & = \frac{x_{A}(1+\epsilon^2)^2}{y} S_{++}(1) \sin(\phi), \\
   \alpha_1 (\phi) & = c_0^{BH}+c_1^{BH} \cos({\phi})+c_2^{BH} \cos(2\phi), \\ 
   \alpha_2 (\phi) & = \frac{x_{A}(1+\epsilon^2)^2}{y}  \left( 
      C_{++}(0) +  C_{++}(1) cos(\phi) \right), \\
   \alpha_3 (\phi) &= \frac{x^{2}_{A}t(1+\epsilon^2)^2}{y} {\mathcal P}_1(\phi) 
      {\mathcal P}_2(\phi) \cdot 2 \frac{2-2y+y^2 + \frac{\epsilon^2}{2}y^2}{1 + 
      \epsilon^2},
\end{align}
where $x_{A} = \frac{x_{B}M_{N}}{M_{A}}$ with $M_{A}$($M_{N}$) is the $^4$He 
(nucleon) mass, $\epsilon = \frac{2x_{A}M_{A}}{\sqrt{Q^{2}}}$ and 
$y=\frac{Q^{2}}{2x_{A}M_{A}E_{beam}}$, $\mathcal{P}_1(\phi)$ and $\mathcal 
{P}_2(\phi)$ are the Bethe-Heitler propagators. The factors $c_{0,1,2}^{BH}$, 
$c_0^{DVCS}$, $c_{0,1}^{INT}$ and $s_1^{INT}$ are the Fourier coefficients of 
the BH, and $S_{++}(1)$, $C_{++}(0)$, and $C_{++}(1)$ are the Fourier harmonics 
in the leptonic tensor.  The explicit expressions of these terms can be found 
in \cite{Belitsky:2008bz} and show that, by using the $\sin(\phi)$ and 
$\cos(\phi)$ contributions, it is possible to extract $\Im m(\mathcal{H}_{A})$ 
and $\Re e(\mathcal{H}_{A})$ from the beam spin
asymmetry.

@@

The $Q^2$, $x_B$, and $t$ dependencies of the $^4$He CFF $\mathcal{H}_A$ 
extracted from the fit to the azimuthal dependence of $A_{LU}$ are shown in 
Figure \ref{fig:CFF_HA}. Curves on the graphs are model calculations, labelled 
{\it convolution} and {\it off-shell}. In the convolution model 
\cite{Vadim_priv}, the nucleus is assumed to be composed of non-relativistic 
nucleons, each interacting independently with the probe. The Convolution-Dual 
model is based on nucleon GPDs from the dual parametrization 
\cite{Guzey:2006xi}, where the Convolution-VGG uses nucleon GPDs  from the VGG 
model and is based on the double distributions ansatz \cite{DD_model}. The 
off-shell model \cite{GonzalezHernandez:2012jv} relies on the impulse 
approximation and uses advanced spectral functions of  nuclei that account for 
all configurations of the final nuclear system and the binding effects between 
the nucleons.

### 2017-02-25 for_eg6_group/incoh-2/Incoh.tex
added a subdirectory for eg6 comments on the coherent paper and another subdirectory for the incoherent channel inestigation.

\begin{figure}[h!]
\includegraphics[height=5.0cm]{fig/T_tprime_Coh.png}
\includegraphics[height=5.0cm]{fig/T_tprime_InCoh.png}
\caption{On the left: the coherent relative difference between $t$ and $t'$.  
On the right: the incoherent relative difference.}
\label{fig:tprime}
\end{figure}

@@

>>>>

%\begin{figure}[h!]
%\includegraphics[height=5.0cm]{fig/T_tprime_Coh.png}
%\includegraphics[height=5.0cm]{fig/T_tprime_InCoh.png}
%\caption{On the left: the coherent relative difference between $t$ and $t'$.  
%On the right: the incoherent relative difference.}
%\label{fig:tprime}
%\end{figure}

\begin{figure}[h!]
\includegraphics[height=20.0cm]{fig/bins_InCoh_t_tc_tprime.pdf}
\caption{t, tc, and t' for incoherent DVCS events}
\label{fig:tprime}
\end{figure}

@@

\newpage
\newpage
\newpage
\newpage
\newpage
\section*{t, tc, and t' for coherent and incoherent DVCS channels}

%\begin{figure}[h!]
%\includegraphics[height=20.0cm]{fig/t_tc_trpime_Coh_bins.pdf}
%\caption{}
%\label{fig:}
%\end{figure}
